Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-08-26 paper/1_Initial/manuscript.qmd
added authors

table |> 
  dplyr::rename("Age (Mean  ± SD)" = Age,  "Female %" = Female_Percentage)  |> 
  flextable() |> 
  set_table_properties(layout = "autofit", opts_pdf=list(arraystretch=1)) |> 
  theme_apa() 
```

>>>>

table |>
  dplyr::rename("Age (Mean  ± SD)" = Age, "Female %" = Female_Percentage) |>
  flextable() |>
  set_table_properties(layout = "autofit", opts_pdf = list(arraystretch = 1)) |>
  theme_apa()
```
